% lst_models paper - ICAIF-style ACM submission (Doc A contract v1.2)
% Submission build: sigconf + review + anonymous; 8 pages TOTAL incl. figures+refs.
\documentclass[sigconf,review,anonymous]{acmart}

% Package whitelist per Doc A §2 (booktabs, graphicx, siunitx, amsmath).
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{amsmath}

% Float/caption separation tightened (layout only; no content, numbers, or
% packages changed) to hold the hard 8-page limit while every figure renders.
% Wrapped in \AtBeginDocument so it overrides the acmart class defaults.
\AtBeginDocument{%
  \setlength{\textfloatsep}{4pt plus 2pt minus 2pt}%
  \setlength{\floatsep}{4pt plus 2pt minus 2pt}%
  \setlength{\intextsep}{4pt plus 2pt minus 2pt}%
  \setlength{\abovecaptionskip}{2pt}%
  \setlength{\belowcaptionskip}{0pt}%
}

% Custom macros: <=10, all here, all commented (Doc A §2).
\newcommand{\macrofone}{macro-F1}          % consistent metric name
\newcommand{\pp}{\,\textrm{pp}}             % percentage points (math+text safe)
\newcommand{\numseeds}{2}                   % official validation seeds (ledger §1)

% Submission build: suppress the drafting-only \shownote{} editorial/VERIFY notes
% carried in main.bbl so they do not print in the final references. Defined before
% \bibliography so the .bbl's \ifx...\undefined guard sees it and keeps this. Remove
% this line to restore the notes during drafting.
\def\shownote#1{}

\begin{document}
\raggedbottom

% Title per Doc B v1.5 title direction: evaluation-discipline framing with the
% fixed task term "intraday stock direction classification" (replaces the retired
% AI-template skeleton "Guarded Chronological Evaluation of Weak Intraday
% Directional Signals"). Still evaluation-discipline, not protocol-as-product. No
% title footnotes for draft markers: acmart prints them under the title (blind
% gate, Doc A section 7).
\title{Small Edges, Strict Boundaries: A Chronological Evaluation of Intraday Stock Direction Classification}

% Authors intentionally omitted: anonymous submission build.

\begin{abstract}
In intraday 5-minute stock-direction classification, validation contact,
leakage, and repeated comparison can inflate \macrofone{} gains. We
contribute, not a new model: a strict pre-registered protocol; under it, a
small, sign-consistent TCN margin over same-row baselines; and calibration and
activity-regime diagnostics that locate where it holds and breaks. Before
scoring, we freeze the label, no-trade band, chronological splits, roster, and
decision rules. Each model is compared with a same-row stratified dummy, and
each validation look is logged in a counted validation-budget ledger. On the
frozen validation split, a predeclared TCN exceeds
that dummy by 1.69\pp{} in \macrofone{} (two-seed mean, 1.63\pp{} at the worse
seed; too few to quantify variance). A separate guarded walk-forward over the
post-2017 segment, historically contacted and not a clean test, stays positive
(row-pooled $+0.636\pp$) and clears a deliberately weak predeclared bar. A
descriptive CSCV/PBO readout of $0.514$, near a coin flip, is too coarse to
rule overfitting in or out. The residual sits in the calmest bars and drops
below the balanced random prior on the most active bars in both windows (one
historically contacted), a pattern we cannot separate from a bid-ask-bounce
artifact. We measure \macrofone{}, not economic value. The protocol is shown on
five large-cap US equities as one near-null case with no known-signal positive
control, so its sensitivity to a genuine signal is untested.
\end{abstract}

% CCS concepts + keywords (mandatory for papers > 2 pages, Doc A §10).
% VERIFY-BEFORE-SUBMIT: the \ccsdesc descriptions/significance below are final,
% but regenerate the CCSXML and confirm the numeric concept_id values via the ACM
% CCS tool (https://dl.acm.org/ccs); the ids are best-effort and do not affect the
% rendered PDF (only ACM DL ingestion).
\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10010147.10010257</concept_id>
       <concept_desc>Computing methodologies~Machine learning</concept_desc>
       <concept_significance>500</concept_significance>
   </concept>
   <concept>
       <concept_id>10002950.10003648</concept_id>
       <concept_desc>Mathematics of computing~Probability and statistics</concept_desc>
       <concept_significance>300</concept_significance>
   </concept>
   <concept>
       <concept_id>10010405.10010444.10010087</concept_id>
       <concept_desc>Applied computing~Economics</concept_desc>
       <concept_significance>300</concept_significance>
   </concept>
</ccs2012>
\end{CCSXML}
\ccsdesc[500]{Computing methodologies~Machine learning}
\ccsdesc[300]{Mathematics of computing~Probability and statistics}
\ccsdesc[300]{Applied computing~Economics}
\keywords{intraday direction classification, chronological validation,
no-trade band, model calibration, selective classification, backtest overfitting}

\maketitle

\input{sections/01_intro}
\input{sections/02_related}
\input{sections/03_protocol}
\input{sections/04_models}
\input{sections/05_setup}
\input{sections/06_results}
\input{sections/07_guarded_walkforward}
\input{sections/08_diagnostics}
\input{sections/09_limitations_conclusion}

% --- Endmatter ---------------------------------------------------------
% GenAI usage statement (mandatory, ACM 2026; template Doc A §8).
\section*{Generative AI Usage Statement}
Generative AI tools were used to assist with literature search, drafting
and translating prose from the authors' notes, editing for style, generating
figure-plotting code, and reviewing claim consistency, citations, provenance,
and final-form issues. All experimental design, code execution, results, and
claims were produced and verified by the authors. All
AI-assisted text was reviewed, fact-checked against the project's
experiment artifacts, and revised by the authors, who take full
responsibility for the content.

% Acknowledgments: REMOVED in submission build (Doc A §7 blind gate).

\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

\end{document}
