% Introduction (Option-2 finding-forward framing). Live section, input by main.tex.
% Revised through the Option-2 per-section loop (logic-reviewer + writing-reviewer).
% Spine: a weak but conditional edge survives strict evaluation; we map where it
% holds and where it inverts. Confident on METHOD, honest on NUMBERS. Every number
% binds to claims ledger v1.13; three evidence domains kept separate (no fusion).
\section{Introduction}

A small directional signal in intraday five-minute stock prices can survive careful
scrutiny, or it can be an artifact of how the evaluation was run. On a frozen
validation split, a predeclared temporal convolutional network exceeds a same-row
stratified-dummy floor by 1.69\pp{} in \macrofone{}, a margin that sits just above a
near-even floor. Validation contact, temporal leakage, and repeated model comparison
each manufacture gaps of that size
\cite{kapoor2023leakage,bailey2016probability,harvey2016cross}, so the number alone
settles nothing. We ask what remains of such an edge once the evaluation is made
strict, and where it lives.

We answer with an evaluation protocol that fixes the terms of the test before any
model is scored. It freezes the label, no-trade band, chronological day-block splits,
model roster, same-row dummy floor, and a counted validation-look budget, then scores
each model against that floor. The protocol makes no architecture claim and selects no
final model; the model families exist to exercise it. Financial machine-learning
studies fit flexible models to stock and limit-order-book prediction
\cite{gu2020empirical,zhang2019deeplob}, while a parallel literature shows how adaptive
validation and backtest overfitting inflate the gains they appear to deliver
\cite{kapoor2023leakage,bailey2016probability,harvey2016cross}. We take the step before
a trading backtest and ask what a return-free, drop-neutral direction-classification
estimand yields under these controls.

Run under the protocol, that estimand yields a small and uneven edge. On the frozen
validation split the predeclared TCN primary's two-seed mean margin over the same-row
stratified dummy is 1.69\pp{} in \macrofone{}, dropping to 1.63\pp{} at the worse seed.
\numseeds{} seeds are too few to quantify variance. The pooled margin's descriptive
block-bootstrap interval excludes zero. As a point estimate the gain holds in all five
tickers, though the per-ticker values spread widely. Train-inner control comparisons across four control rows (two of them
last-step ablation controls) show a 0.66\pp{} spread, smaller than the 1.69\pp{}
official-validation margin though not a full-family comparison. That spread fixes the
edge's modest size against a near-even floor.

Past the validation boundary, a guarded walk-forward applies the same discipline. This
is not a clean test: the post-2017 segment is a non-independent confirmation of the
validation-frozen primary, scored more than once within the project
\cite{dwork2015reusable}. The predeclared primary clears a deliberately weak stability
bar there, with a row-pooled delta of +0.636\pp{}. A descriptive multiplicity check
returns a probability of backtest overfitting of 0.514, near a coin flip. The guarded
readout corroborates the sign on its own segment; it does not strengthen the validation
claim, and the three domains stay separate.

Because neither readout turns a thin margin into a strong one, the protocol's most
informative outputs are two diagnostics, not the headline number: whether the
confidence scores are usable, and where the edge concentrates. Calibration error is
small while its resolution is near-zero (equal-mass ten-bin ECE \(\approx 0.010\)),
so the confidence scores cannot define an operating rule. Partitioned by activity, the edge
is largest on the calmest bars (low-activity tercile, +5.43\pp{} over dummy) and falls
below the balanced random prior on the most active ones (high-activity tercile,
\macrofone{} \(\approx 0.483\)). The same low-to-high pattern recurs in the guarded
2017--2024 window. Here activity means eligible-row count under the no-trade band, not
volume or liquidity. A bid-ask-bounce alignment we cannot rule out \cite{roll1984simple}
keeps the pattern a diagnostic boundary rather than model-attributable predictability.

The paper therefore makes three contributions: a pre-registered evaluation protocol; a
battery of calibration, regime, and robustness diagnostics; and a worked case that
exercises them end to end. In that case a pre-registered model clears its same-row dummy
by a small but consistent margin, positive in all five tickers, which the diagnostics
then resolve as near-null overall and regime-fragile. The case is deliberately narrow: five large-cap US
survivors, \numseeds{} seeds, and \macrofone{} only, with no profit-and-loss, cost
model, or known-signal positive control. Whether the same protocol flags these signs as
absent on a genuine signal is the positive-control next step. What the protocol records
is the contribution: estimand sensitivity, a weak stability bar, multiplicity fragility,
and a conditional sign that a headline-only readout would hide. The diagnostics map where
this edge persists and where it reverses.
