% Budget/contract: 0.7 page. Tier-G wording only. Use Stage 05 local-derived
% paper-facing evidence first: 05_thesis_synthesis_report, 05_validation_budget_ledger,
% 05_estimand_contrast, 05_multiplicity_discount, and 05_row_pooled_* addenda.
% Upstream raw v2_1_decision_record.json remains Drive-only provenance. Must state
% guarded (non-independent); not a clean test; no final model selected;
% threshold bar = >=2/7 positive periods plus positive pooled delta; 5/7 is descriptive.
% Pilot round 2 (logic+writing review): fixed domain fusion (guarded-only stability),
% removed sec8 preview restatement, split over-cap sentences, standardized "predeclared".
\section{Guarded Walk-Forward Readout}\label{sec:guarded}

\paragraph{What the guarded readout is.}
Past the validation boundary, we run a guarded walk-forward readout over seven
consecutive 12-month periods on the post-2017 segment. The readout confirms the
already-frozen primary over expanding-window periods that share rows and a fixed
survivor universe. No final model is selected, so it is a non-independent
confirmation rather than a future-blind test. The post-2017 segment was also scored
more than once within the project. An earlier walk-forward run preceded the bound re-run
reported here, so the holdout is spent and its second reading is a reuse, not a fresh
look \cite{dwork2015reusable}. For both reasons the readout makes no clean-test,
out-of-sample-proof, or final-model claim. The other roster rows are comparison
evidence, never ranked and never selected.

\paragraph{The bar is a weak floor, not the observed count.}
The predeclared TCN primary met the predeclared guarded stability criteria. The
criteria are an intentionally weak floor: at least two of seven periods positive in
\macrofone{} over the same-row stratified dummy, and a positive pooled delta. Under an
independent fair-coin null the two-of-seven clause alone passes about 94\% of the time,
so the bar only prevents post hoc relaxation. The observed five-of-seven positive
periods (Figure~\ref{fig:validation_deltas}, Panel B) are descriptive context, not
certification and not the bar. Because the edge is near-null, we read the guarded readout
as one worked instance of the protocol, not as evidence of a durable edge.

Behind that pass the period-level deltas are uneven. The readout comprises 56 guarded
scoring events (seven periods, four families, \numseeds{} seeds), judged on the
primary's rows alone; the addenda only re-aggregate the frozen per-period prediction
dumps from the predeclared walk-forward refits. The primary's 2020--21 and 2022--23 period
means fall in the COVID and bear-market windows, and both are negative. The 2022--23
period also reverses sign across the two seeds. With only \numseeds{} seeds we cannot
quantify that dispersion, so the per-period readout is not even seed-stable there.

\paragraph{The headline delta is estimand-sensitive.}
The headline delta moves with the aggregation choice, so we report two units rather
than naming either as the number. The binding quantity is the row-pooled delta over
the protocol row-union: $+0.636\pp{}$ in \macrofone{} over the stratified dummy. Its
equal-weight-per-period companion is $+0.550\pp{}$, small under either unit. Because
the bar tests only the sign of a positive pooled delta, it is insensitive to this choice.

Repeated comparison across the roster could also inflate this small edge, so the
protocol applies a multiplicity discount on the binding row-pooled estimand. The discount is an
odd-block CSCV/PBO adaptation ($n_{\text{trials}}{=}4$, $n_{\text{blocks}}{=}7$) that
departs from the canonical symmetric form. These are descriptive discounts, not significance tests
\cite{bailey2014pseudo,bailey2016probability,harvey2016cross}.

\paragraph{Pre-registration, not peak performance, survives multiplicity.}
Across the four-family by seven-period guarded roster the CSCV probability of backtest
overfitting is $0.514$, near a coin flip. The numerically largest family mean belongs to
LightGBM at $+0.726\pp{}$, yet its period lower bound is negative ($-0.030\pp{}$). Only
the predeclared TCN primary has a period lower bound above zero ($+0.047\pp{}$). Under
the multiplicity discount the predeclared candidate survives, not the highest scorer,
and still no family is selected. Consistent with that, the validation-budget
ledger keeps the contact asymmetry explicit: \numseeds{} official-validation scoring
events against 56 guarded events, all with \texttt{for\_selection=false}.

\paragraph{The guarded sign is small but stable.}
On its own segment that sign holds: its pooled block-bootstrap
interval, $[0.24, 1.02]\pp{}$, excludes zero as a descriptive resampling interval rather
than a significance test. The sign survives every leave-one-period-out and
leave-one-ticker-out drop (worst cases $+0.538\pp{}$ and $+0.514\pp{}$). A within-day
label-shuffle sentinel collapses the delta toward a negative null, so
the edge is not a within-day-leakage artifact. These checks are descriptive and stay
under the multiplicity discount above. A stable pooled sign can still hide a direction
that flips across conditions, and Section~\ref{sec:diagnostics} resolves the same-row
edge by activity to find that boundary. What survives strict evaluation here is a
predeclared sign, not a strong number: the direction holds weakly on its own segment,
and only the predeclared candidate keeps a positive period lower bound.
