% Budget/contract: 0.35 page. Required limitations: n=2 seeds, single market,
% five tickers, fixed band=3.0 bps and horizon=9 without sensitivity scan,
% macro-F1 is not economic value, residual Roll(1984) microstructure risk, and
% guarded readout is non-independent, not a clean test.
\section{Conclusion and Limitations}
\label{sec:limitations}

The contribution is an evaluation protocol with three working parts. A pre-score
freeze, same-row dummy floors, and a budget ledger keep the readout auditable
whatever the outcome. Under that protocol the predeclared frozen TCN primary
holds a small margin over its same-row baselines, consistent in pooled sign and
positive in all five tickers. The margin is uneven in size across tickers and
regimes, an evaluation finding, not an architecture claim. Beyond the protocol itself, calibration and regime diagnostics bound and interpret
that margin, and the confidence scores rank cases too weakly to define an
operating rule. We name the magnitudes to be scrutinized rather than sold. The 1.69\pp{}
validation margin is a thin edge above a near-even floor. In the separate
guarded readout, the 0.636\pp{} row-pooled delta over the same-row dummy is
likewise thin, and its backtest-overfitting probability is a near-coin 0.514. The validation margin even flips sign across
activity, from 5.43\pp{} on the calmest bars to 1.54\pp{} below the dummy on the
most active, a conditional sign a headline-only readout would omit.

The case is deliberately narrow. The protocol runs on one near-null case with no
known-signal positive control, so its sensitivity to a genuine signal is untested.
The official validation readout rests on \numseeds{} seeds, too few for
seed-to-seed variance \cite{bouthillier2021accounting,picard2021torch}, and the
Student-$t$ lower bound shipped with the decision record is provenance, not a
decision criterion. The scope is a single market and five large-cap survivors of
the 1998--2024 span, so any positive readout is entangled with survivor selection
and does not extend to a broader panel.

The remaining limitations concern construct and claim scope. The no-trade band
($3.0$ bps) and the label horizon (nine bars) are pre-registered and frozen, with
no threshold or horizon sensitivity scan. \macrofone{} is a classification
readout, not economic value, and with no execution model or transaction-cost
accounting no margin here, validation, train-inner control, or guarded, is a
trading claim. The guarded walk-forward is a non-independent confirmation, not a
clean test, and no final model is selected. Its family margins are fragile. Under
the descriptive multiplicity discount on the binding row-pooled estimand, the
discounted per-period lower bound falls below zero for every family except the
predeclared primary. That is not a like-for-like ranking, since the non-primary
rows are post-hoc maxima and the primary a frozen profile, and the descriptive
PBO is too coarse to rule overfitting in or out. The calm-bar
concentration of Section~\ref{sec:diagnostics} carries one open risk. The closing
price $\text{close}[t]$ enters both the most-recent-return feature and the
forward-label denominator. A bid-ask bounce, largest relative to the small
returns of the calmest bars, is therefore an alternative this classification-only
evaluation cannot quantify \cite{roll1984simple,lo1990nonsynchronous}. The
label-shuffle sentinel rules out within-day leakage and day-base-rate artifacts
but has no power against that bounce. The discriminating control, a half-spread
proxy against the $3.0$ bps band, needs raw five-minute bars the dump does not
carry, so we defer it.

The defined next step is a known-signal positive control: confirming that the
same protocol flags these signs as absent when a genuine signal is
present. The outcome here is a weak, conditional readout, not a model or a trading
system; the transferable contribution is the evaluation protocol and the diagnostics
that locate where such an edge holds and breaks.
