% lst_models paper - ICAIF-style ACM submission (Doc A contract v1.2)
% Submission build: sigconf + review + anonymous; 8 pages TOTAL incl. figures+refs.
\documentclass[sigconf,review,anonymous]{acmart}

% Package whitelist per Doc A §2 (booktabs, graphicx, siunitx, amsmath).
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{amsmath}

% Float/caption separation tightened (layout only; no content, numbers, or
% packages changed) to hold the hard 8-page limit while every figure renders.
% Wrapped in \AtBeginDocument so it overrides the acmart class defaults.
\AtBeginDocument{%
  \setlength{\textfloatsep}{4pt plus 2pt minus 2pt}%
  \setlength{\floatsep}{4pt plus 2pt minus 2pt}%
  \setlength{\intextsep}{4pt plus 2pt minus 2pt}%
  \setlength{\abovecaptionskip}{2pt}%
  \setlength{\belowcaptionskip}{0pt}%
}

% Custom macros: <=10, all here, all commented (Doc A §2).
\newcommand{\macrofone}{macro-F1}          % consistent metric name
\newcommand{\pp}{\,\textrm{pp}}             % percentage points (math+text safe)
\newcommand{\numseeds}{2}                   % official validation seeds (ledger §1)

% Submission build: suppress the drafting-only \shownote{} editorial/VERIFY notes
% carried in main.bbl so they do not print in the final references. Defined before
% \bibliography so the .bbl's \ifx...\undefined guard sees it and keeps this. Remove
% this line to restore the notes during drafting.
\def\shownote#1{}

\begin{document}
\raggedbottom

% Title per Doc B v1.5 title direction: evaluation-discipline framing with the
% fixed task term "intraday stock direction classification" (replaces the retired
% AI-template skeleton "Guarded Chronological Evaluation of Weak Intraday
% Directional Signals"). Still evaluation-discipline, not protocol-as-product. No
% title footnotes for draft markers: acmart prints them under the title (blind
% gate, Doc A section 7).
\title{Small Edges, Strict Boundaries: A Chronological Evaluation of Intraday Stock Direction Classification}

% Authors intentionally omitted: anonymous submission build.

\begin{abstract}
In intraday five-minute stock-direction classification, a weak edge can survive
strict evaluation yet hold only under conditions. We establish this with an
evaluation protocol fixed before any model is scored. It freezes the label,
no-trade band, chronological splits, roster, same-row dummy floor, and a counted
validation-look budget. The controls matter because validation contact, leakage,
and repeated comparison can inflate \macrofone{} on a target that sits just above
a stratified-dummy floor. On the frozen validation split, a predeclared temporal
convolutional network exceeds the same-row stratified dummy by 1.69\pp{} in
\macrofone{} (two-seed mean, 1.63\pp{} at the worse seed; \numseeds{} seeds cannot
quantify variance). On a separate guarded, non-independent walk-forward over
post-2017 (expanding windows share rows), which is not a clean test, the same
candidate stays positive at $+0.636\pp{}$ row-pooled and clears a deliberately
weak bar. A descriptive CSCV/PBO of $0.514$ leaves overfitting unresolved. The
candidate's edge is also conditional: it concentrates in the calmest bars and
falls below the balanced random prior on the most active ones. This low-to-high
pattern recurs across both windows, though we cannot yet separate it from a
bid-ask-bounce artifact. We measure \macrofone{}, not economic value, on five
large-cap US survivors with no known-signal positive control. The contribution is
the evaluation discipline and a map of where a thin edge holds and where it
inverts. Whether the protocol also shows such signs are absent on a genuine
signal is the next test.
\end{abstract}

% CCS concepts + keywords (mandatory for papers > 2 pages, Doc A §10).
% VERIFY-BEFORE-SUBMIT: the \ccsdesc descriptions/significance below are final,
% but regenerate the CCSXML and confirm the numeric concept_id values via the ACM
% CCS tool (https://dl.acm.org/ccs); the ids are best-effort and do not affect the
% rendered PDF (only ACM DL ingestion).
\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10010147.10010257</concept_id>
       <concept_desc>Computing methodologies~Machine learning</concept_desc>
       <concept_significance>500</concept_significance>
   </concept>
   <concept>
       <concept_id>10002950.10003648</concept_id>
       <concept_desc>Mathematics of computing~Probability and statistics</concept_desc>
       <concept_significance>300</concept_significance>
   </concept>
   <concept>
       <concept_id>10010405.10010444.10010087</concept_id>
       <concept_desc>Applied computing~Economics</concept_desc>
       <concept_significance>300</concept_significance>
   </concept>
</ccs2012>
\end{CCSXML}
\ccsdesc[500]{Computing methodologies~Machine learning}
\ccsdesc[300]{Mathematics of computing~Probability and statistics}
\ccsdesc[300]{Applied computing~Economics}
\keywords{intraday direction classification, chronological validation,
no-trade band, model calibration, selective classification, backtest overfitting}

\maketitle

\input{sections/01_intro}
\input{sections/02_related}
\input{sections/03_protocol}
\input{sections/04_models}
\input{sections/05_setup}
\input{sections/06_results}
\input{sections/07_guarded_walkforward}
\input{sections/08_diagnostics}
\input{sections/09_limitations_conclusion}

% --- Endmatter ---------------------------------------------------------
% GenAI usage statement (mandatory, ACM 2026; template Doc A §8).
\section*{Generative AI Usage Statement}
Generative AI tools were used to assist with literature search, drafting
and translating prose from the authors' notes, editing for style, generating
figure-plotting code, and reviewing claim consistency, citations, provenance,
and final-form issues. All experimental design, code execution, results, and
claims were produced and verified by the authors. All
AI-assisted text was reviewed, fact-checked against the project's
experiment artifacts, and revised by the authors, who take full
responsibility for the content.

% Acknowledgments: REMOVED in submission build (Doc A §7 blind gate).

\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

\end{document}
