% Budget/contract: 0.35 page. Six threads: financial prediction baselines;
% leakage and chronological validation; model-family positioning; selective
% classification and calibration; multiplicity/backtest overfitting; microstructure
% caveats. Keep leakage, backtest-overfitting, and microstructure threads.
\section{Related Work}

Asset-pricing and equity-prediction studies apply machine-learning models to
financial panels \cite{gu2020empirical,fischer2018deep}. Intraday
limit-order-book work applies related classifiers to high-frequency streams
\cite{zhang2019deeplob}. We reuse this work for a narrower estimand:
drop-neutral, 5-minute direction classification with a same-row stratified dummy
floor. A \macrofone{} margin here is classification evidence, not investment
performance.

A primary methodological risk is validation contact. Leakage in
machine-learning studies and decision-time backtest leakage show that adaptive
validation can inflate apparent performance
\cite{kapoor2023leakage,zhang2026whenalpha}; reusable-holdout and
preregistration work supplies validity-preserving guards
\cite{dwork2015reusable,hofman2023preregistration}. Chronological evaluation is
the temporal guard \cite{hyndman2021forecasting}. Finance addresses
data-snooping with backtest-overfitting probability, reality-check tests, and
multiple-testing corrections
\cite{lopezdeprado2018advances,bailey2014pseudo,bailey2016probability,harvey2016cross,white2000reality,sullivan1999datasnooping}.
We combine these standard guards for this return-free \macrofone{} estimand:
fixed label and band, chronological day blocks with day-local windows, a
same-row stratified dummy, and a validation-budget ledger. We exercise it on a
single near-null case, not a known-signal control. Return-based benchmarks and
investing-strategy studies score later economic stages
\cite{zhang2026whenalpha,li2026finsaber}; our readout audits the upstream
classification gate.

The model families are intentionally ordinary. TCNs, decomposition linear models,
and gradient-boosted trees are established sequence or tabular baselines
\cite{bai2018empirical,zeng2023dlinear,ke2017lightgbm,grinsztajn2022tree}. We use
them to exercise the protocol; we make no architecture claim and no
final-model selection.

Selective classification and calibration enter here only as an adverse diagnostic
on whether confidence scores rank cases usefully
\cite{geifman2017selective,guo2017calibration,traub2024overcoming,chalkidis2021trading}.
Brier-score decomposition separates calibration error from resolution
\cite{brier1950verification,murphy1973vector}. A second boundary is
microstructural. Prior intraday-return studies document cross-sectional
periodicity, time-varying short-horizon predictability, and seasonality
\cite{heston2010intraday,henkel2011timevarying,bogousslavsky2016infrequent}.
That literature is a foil for our condition map: its predictability is tied to
timing, higher-activity states, or seasonal rebalancing, not the calm slice where
our edge concentrates. Bid-ask bounce can create row-level structure preserved by
within-day permutation
\cite{roll1984simple,lo1990nonsynchronous}. Our controls cannot yet rule it out,
so we frame the activity-tercile result as a conditional limitation.
