% Budget/contract: 0.6 page. Four paper-facing families only: TCN primary,
% standard-DLinear, MS-DLinear+TCN, and LightGBM. MLP appears only as a
% train-inner control row where needed; do not present LSTM as a route model.
% Source: protocol 02 + configs/models/.
\section{Models}

The fixed roster only exercises the evaluation procedure; only the TCN is primary. We score exactly four families: a temporal convolutional
network, a decomposition-linear model, a decomposition-convolutional hybrid, and
gradient-boosted trees
\cite{bai2018empirical,zeng2023dlinear,ke2017lightgbm,grinsztajn2022tree}. None
is a known-signal positive control. The roster can therefore show that the
procedure does not manufacture an edge on a near-null case. It cannot show that
it would catch a real one.

The predeclared primary is a temporal convolutional network
\cite{bai2018empirical} in a \texttt{tcn\_tiny} configuration: two residual
blocks of 16 channels each, kernel size \(2\), and learning rate \(10^{-3}\).
Standard DLinear (Std-DLinear) splits each input window into trend and residual components, each fed
to its own linear head before they are summed \cite{zeng2023dlinear}. The hybrid
pairs a multi-scale DLinear branch (MS-DLinear) with a small
residual TCN branch (jointly, MS-DLinear+TCN); it is an alternative-architecture
roster family, not a contributed model. The hybrid's MS-DLinear branch joins
multiple decomposition kernels as in
series-decomposition forecasters \cite{wu2021autoformer,zhou2022fedformer}. The fourth family is LightGBM \cite{ke2017lightgbm}, a gradient-boosted
tree run as a tabular baseline on windowed features \cite{grinsztajn2022tree}.

The roster and the primary-versus-fallback rule are predeclared, and the
train-inner search runs entirely before any validation or guarded readout. That
search instantiates the predeclared TCN configuration above and reserves LightGBM
as the primary-slot fallback for mechanical or reconstruction failures. None
occurred, so the fallback never fires. Its output is frozen ahead of both
readouts, and neither the validation nor the guarded readout selects a final
model. On the guarded row-pooled mean some roster alternatives show numerically
higher deltas than the predeclared TCN primary, but only post hoc and not
like-for-like; the TCN is the lone pre-committed frozen primary. No recurrent model enters the roster. The last-step multilayer perceptron
(\texttt{last\_step\_mlp}) appears only as a train-inner control, not a scored
family. The four families share the data, seeds, and frozen designation that the
next section fixes.
