% Budget/contract: 0.45 page. Table 1 dataset stats; HPO protocol; n=2 official
% validation seeds (state honestly); frozen-params selection rule; device one-liner.
% Date ranges closed in claims ledger sec.1 (source: stage00 config + protocol 00).
\section{Experimental Setup}
\label{sec:setup}

We fix the data and the train-inner search settings the protocol section defers
here; Table~\ref{tab:dataset} lists the frozen statistics. The study uses five
large-cap US equities (CSCO, JPM, KO, MSFT, WMT) as 5-minute bars resampled from
1-minute data. The
chronological split places 736{,}685 labeled target rows in the train interval
(1998-01-02 through 2013-09-16, end exclusive) and 151{,}064 in the official
validation interval (2013-09-16 through 2017-01-25, end exclusive). Per-ticker
validation counts span $\approx$29.9k--30.8k. Labels use a 9-bar horizon and a
3.0\,bps no-trade band. The input is a 20-bar window over the
\texttt{price\_volume\_time} feature set, the output of the train-inner feature
and window search; \texttt{price\_action\_core} is the registered fallback
feature set. This step shortlists the feature set and window only; family
designation is the separate train-inner step below.

\begin{table}[t]
  \caption{Frozen dataset statistics. Counts are eligible binary target rows
    after the no-trade band invalidates near-flat rows, over end-exclusive
    chronological day blocks. The holdout from 2017-01-25 received zero
    validation-phase contact (\texttt{holdout\_test\_contact}{=}false).}
  \label{tab:dataset}
  \begin{tabular}{ll}
    \toprule
    Property & Value \\
    \midrule
    Tickers & CSCO, JPM, KO, MSFT, WMT (5) \\
    Frequency & 5-min bars (from 1-min) \\
    Train interval & 1998-01-02 -- 2013-09-16 (excl.) \\
    Validation interval & 2013-09-16 -- 2017-01-25 (excl.) \\
    Train rows & 736{,}685 \\
    Validation rows & 151{,}064 ($\approx$29.9k--30.8k/ticker) \\
    Label horizon & 9 bars \\
    No-trade band & 3.0\,bps \\
    Window $w$ & 20 \\
    Primary feature set & \texttt{price\_volume\_time} \\
    Fallback feature set & \texttt{price\_action\_core} \\
    \bottomrule
  \end{tabular}
\end{table}

This separate train-inner step fixes the predeclared primary and fallback
designation and one profile per family. The frozen feature-window and
train-inner configs, handoff, and readout records bind the grid, search-space
files, inner folds, selected profiles, refit rows, early-stopping source, and
resolved device. The bounded-profiles search is a screening-grade train-inner
selection, not an unconstrained or validation-tuned hyperparameter search. The
official validation readout only characterizes this frozen specification and is
not a model-selection event. The route manifest sets
\nolinkurl{no_final_model_selected=true}. We then report the official validation
outcome in \macrofone{} over $n{=}\numseeds{}$ seeds (101 and 202), refit on the
recorded CUDA device; two seeds are too few to quantify seed-to-seed variance.
