% Budget/contract: 0.7 page. Tier-G wording only. Use Stage 05 local-derived
% paper-facing evidence first: 05_thesis_synthesis_report, 05_validation_budget_ledger,
% 05_estimand_contrast, 05_multiplicity_discount, and 05_row_pooled_* addenda.
% Upstream raw v2_1_decision_record.json remains Drive-only provenance. Must state
% guarded (non-independent); not a clean test; no final model selected;
% threshold bar = >=2/7 positive periods plus positive pooled delta; 5/7 is descriptive.
\section{Guarded Walk-Forward Readout}\label{sec:guarded}

\paragraph{What the guarded readout is.}
To show what the procedure reports past the validation boundary, we run a
guarded walk-forward readout over seven consecutive
12-month periods on the post-2017 segment. Per the seal of
Section~\ref{sec:protocol}, that segment saw no validation-phase contact.
Because the readout confirms the already-frozen primary over expanding-window
periods that share rows and a fixed survivor universe, it is a guarded,
non-independent confirmation, not a future-blind test, and makes no clean-test,
out-of-sample-proof, or final-model claim. The other roster rows are comparison
evidence, never ranked or selected.

\paragraph{The bar is a weak floor, not the observed count.}
The predeclared TCN primary met the predeclared guarded stability criteria.
The criteria are an intentionally weak floor: at least two of seven periods
positive in \macrofone{} over the same-row stratified dummy, and a positive
pooled delta. Under an independent fair-coin null, the two-of-seven clause alone
passes about 94\% of the time, so the bar only prevents post hoc relaxation.
The observed five-of-seven positive periods
(Figure~\ref{fig:validation_deltas}, Panel B) are descriptive context, not
certification and not the bar. Because the edge is near-null, we read the guarded
readout as one worked instance of the procedure, not evidence of a durable edge.
The procedure still reports what a headline-only readout would omit: a weak
floor, a near-even multiplicity-discount readout, and a conditional sign.

Behind that pass, the period-level deltas are uneven. The readout comprises 56
guarded scoring events (seven periods, four roster rows, \numseeds{} seeds); the
decision is judged on the primary's rows alone. The predeclared primary's
2020--21 and 2022--23 period means fall in the COVID and bear-market windows, and
both are negative. The 2022--23 period also reverses sign across the two seeds, a
dispersion \numseeds{} seeds are too few to quantify. The per-period readout is
therefore not even seed-stable there. The addenda only re-aggregate frozen per-period
prediction dumps; the fits are the predeclared V2.1 walk-forward refits that
produced those dumps.

\paragraph{The headline delta is estimand-sensitive.}
The headline delta moves with the aggregation choice, so we report both units.
The binding quantity is the row-pooled delta over the protocol row-union,
\(+0.636\pp\) in \macrofone{} over the stratified dummy; the
equal-weight-per-period companion is \(+0.550\pp\). Because the bar tests only the
sign of a positive pooled delta, it is insensitive to this aggregation choice,
and the headline magnitude is small under either unit.

Repeated comparison across the roster could also inflate this small edge, so we
add a multiplicity discount. On the binding row-pooled estimand, we apply an
odd-block CSCV/PBO adaptation (\(n_{\text{trials}}{=}4\),
\(n_{\text{blocks}}{=}7\)), not the canonical symmetric form. It yields a
descriptive PBO readout of \(0.514\). That value is near a coin flip, too coarse to
rule overfitting in or out \cite{bailey2014pseudo,bailey2016probability}. Only the
predeclared TCN-primary period-LCB is above zero, at \(+0.047\pp\); the
worst-family LCB (Std-DLinear) sits at \(-0.464\pp\) \cite{harvey2016cross}. These are
descriptive discounts, not significance tests. On the row-pooled mean the primary
(\(+0.636\pp\)) is third of four: LightGBM is largest (\(+0.726\pp\)), the hybrid
MS-DLinear+TCN second (\(+0.672\pp\), with the most positive periods at \(6/7\)),
and Std-DLinear fourth (\(+0.513\pp\), \(4/7\)). Yet all three non-primary families
keep a period-LCB below zero. The three non-primary rows are post-hoc within-family
profile maxima while the primary is the pre-committed frozen profile. Neither the
mean ranking nor the period-LCB ranking is therefore a like-for-like family comparison.
The primary's lone positive LCB is consistent with its single pre-committed profile, not
a strongest-family claim, and no final model is selected.

Expanding-window training shares rows across periods, and the universe is a fixed
five-ticker survivor set. The leave-one-out check is therefore largely mechanical
here. We report it only as a descriptive sensitivity, not an independence or
significance claim: the row-pooled delta falls no lower than \(+0.538\pp\) by
period and \(+0.514\pp\) by ticker. The validation-budget ledger keeps the contact asymmetry
explicit, at \numseeds{} official-validation scoring events against 56 guarded
events, all with \texttt{for\_selection=false}. The predeclared primary thus
keeps the sign of its pooled edge under these drop-one perturbations, but only
inside a guarded readout. The diagnostics section then
treats the activity-tercile pattern as a diagnostic boundary. The same-row
edge is largest in the calmest bars and drops below the balanced random prior in
the most active ones. An open microstructure confound, however, prevents attributing
that pattern to the model.
